When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-29 doc/paper/vpd_et_paper.tex
made fig5 two panels so show converse with lai on x axis, debugging now
about to swithc up legend terms

Before diving into calculated values of $\frac{\partial \; ET}{\partial \; D}$, it is useful to consider the functional form of Equation \ref{d_et}. There are three terms: a scaling term for the full expression we will call Term 1 ($\frac{g_a \; P}{T(\Delta + \gamma)}$), a relatively constant offset we will call Term 2 ($\frac{c_p}{R_{air}}$), and a variable term we will call Term 3 ($\frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right)$). All variables are constant, so the relative magnitude between Term 2 and Term 3 will determine the sign of the derivative, while Term 1 will scale the expression larger or smaller.

@@

Figure \ref{scale_vary}A shows Term 1 normalized by mean $g_a$ (calcualted for each plant functional type), and confirms that much of the relative variability of Term 1 is contained in the $g_a$ term's relative variability. Additionally, the impact of $T$ on the relative variability increases with increasing $g_a$.

While the relative variability of Term 1 is similiar across PFT, the absolute value of Term 1 varies strongly across PFT. Figure \ref{scale_vary}B shows Term 1 evaluated with the mean $g_a$ for each PFT, and at the range of observed temperatures for each PFT. As expected, for the tree PFTs the Term 1 is much larger and the temperature dependence is much stronger. Additionally, because std$(g_a) \propto \overline{g_a}$, the spread of Term 1 due to $g_a$ variability will be larger, although this is not shown for simplicity. To summarize, the variability of Term 1 will look like Figure \ref{scale_vary}A for each PFT, but the scale of the x and y-axis will increase or decrease according to Figure \ref{scale_vary}B.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig04.pdf}
\caption{Primary sources of variability for Term 1. A) Term 1 normalized by mean $g_a$ for each PFT. B) Term 1 evaluated at mean $g_a$ for each PFT. Temperature range is 5-95th percentile for each PFT. Additionally, stars denote the location of the 25th, 50th, and 75th percentiles.}
\label{scale_vary}
\end{figure}

>>>>

Before diving into calculated values of $\frac{\partial \; ET}{\partial \; D}$, it is useful to consider the functional form of Equation \ref{d_et}. There are three terms: a scaling term for the full expression we will call Term 1 ($\frac{g_a \; P}{T(\Delta + \gamma)}$), a relatively constant offset we will call Term 2 ($\frac{c_p}{R_{air}}$), and a variable term we will call Term 3 ($\frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right)$). All variables are positive, so the relative magnitude between Term 2 and Term 3 will determine the sign of the derivative, while Term 1 will scale the expression larger or smaller.

@@

Figure \ref{scale_vary}A shows Term 1 normalized by mean $g_a$ (calcualted for each plant functional type), and confirms that much of the relative variability of Term 1 is contained in the $g_a$ term's relative variability. Additionally, the impact of $T$ on the relative variability increases with increasing $g_a$. % plot every PFT and show they collapse onto the same vurve?

While the relative variability of Term 1 is similiar across PFT, the absolute value of Term 1 varies strongly across PFT. Figure \ref{scale_vary}B shows Term 1 evaluated with the mean $g_a$ for each PFT, and at the range of observed temperatures for each PFT. As expected, for the tree PFTs (DBF, ENF) Term 1 is much larger and the temperature dependence is much stronger. Systematic differences in observed temperatures also cause difference in the average magnitude of Term 1. For example, ENF experiences on average colder temperatures and is thus more likely to have a larger scaling term. Additionally, because std$(g_a) \propto \overline{g_a}$, the spread of Term 1 due to $g_a$ variability will be larger, although this is not shown for simplicity. To summarize, the variability of Term 1 will look like Figure \ref{scale_vary}A for each PFT, but the scale of the x and y-axis will increase or decrease according to Figure \ref{scale_vary}B.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig04.pdf}
\caption{Primary sources of variability for Term 1. A) Variability within each PFT: Term 1 normalized by mean $g_a$ for each PFT. B) Variability between each PFT: Term 1 evaluated at mean $g_a$ for each PFT. Temperature range is 5-95th percentile for each PFT. Additionally, stars denote the location of the 25th, 50th, and 75th percentiles.}
\label{scale_vary}
\end{figure}

Term 2 minus Term 3 determines the sign and magnitude that the scaling Term 1 is multiplied. If we assume that $c_s$ variability is relatively less than LAI and $D$ variability, then variability within PFT will be soley detmined by LAI and $D$. Figure \ref{term3_within} shows how (Term 2 - Term 3) varies within PFT. Each row is a different PFT, and the first column depects $D$ on the x-axis, evaluated at 5th, 25th, 50th, 75th, and 95th percentiles. The second column has LAI on the x-axis, evaluated at 5th, 25th, 50th, and 95th percentiles of VPD. Within each PFT LAI variability is generally of greater importance to (Term 2 - Term 3)'s variaibility than VPD variaibility. Low VPD and LAI increase the probability of a negative ET response to VPD, and the dependence of the response increases as VPD and LAI get smaller.

Generally, functional forms within each PFT are similiar between each PFT. However, as uWUE increases Term 3 decreases, causing (Term 2 - Term 3) to shift towards positive values. Additionally, the smaller g1 the more important VPD is for the magnitude of Term 3. Fo example, ENF has the smallest g1 (74.31), and the VPD-induced variaibility is of similiar magnitude to the LAI-induced variability. 
% introduce quantitiy uWUE*\overline{LAI}?

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig05.pdf}
\caption{}
\label{term3_within}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig06.pdf}
\caption{}
\label{term3_between}
\end{figure}
